---
title: "MLEARN310_HW1_4"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.	Loading the Data into R


```{r load_mtcars}
data(mtcars)
```

## 2.1 Data Summarization

####  2.1.1 Data Summarization - Stats

```{r summary, echo=FALSE}
summary(mtcars)
```

###  2.1.2 Data Summarization - Structure
``` {r structure, echo=FALSE}
str(mtcars)
```
  
###  2.1.3 Data Summarization - Corrleation

``` {r correlation, echo=FALSE}
cor_matrix = cor(mtcars)
cor_matrix
```

mpg has a strong -ve correlation with cyl , disp, hp and wt and drat ( < -0.5 )

disp has a strong +ve correlation with cyl, hp and wt ( > 0.5 )

drat has a strong -ve correlation with disp and wt ( < -0.5 )

qsec has a strong +ve correlation with vs and mpg ( > 0.5 )

am has a strong -ve correlation with cyl, disp, wt  ( < -0.5 )

am has a strong +ve correlation with gear and drat ( > 0.5 )

carb has a strong +ve correlation with hp and cyl ( > 0.5 )

\newpage
###  2.2 Data Visualization


```{r visualization, echo=FALSE}

boxplot(mtcars$mpg,ylab='mpg')
rug(jitter(mtcars$mpg),side=3)
abline(h=mean(mtcars$mpg4,na.rm=T),lty=2)

library(lattice)
bwplot(mpg ~ cyl, data=mtcars,ylab='mpg',xlab='cyl')
bwplot(mpg ~ hp, data=mtcars,ylab='mpg',xlab='hp')
bwplot(mpg ~ wt, data=mtcars,ylab='mpg',xlab='wt')
```

\newpage

## 3.	Multiple Linear Regression

```{r fit0, echo=TRUE}

fit0 <- lm( mpg ~ as.factor(am), data=mtcars)
summary(fit0)
res0 = residuals(fit0)
plot(jitter(res0)~jitter(mpg), ylab="Residuals", xlab="mpg", data=mtcars)
abline(0,0)
```
**Multiple R-squared:  0.3598**
\newpage
```{r fit1, echo=TRUE}

fit1 <- lm( mpg ~ hp + wt + disp + gear, data=mtcars)
summary(fit1)
res1 = residuals(fit1)
plot(jitter(res1)~jitter(mpg), ylab="Residuals", xlab="mpg", data=mtcars)
abline(0,0)
```
  
**Multiple R-squared:  0.8371**
\newpage
```{r fit2, echo=TRUE}
fit2 <- lm( mpg ~ hp + wt + drat + as.factor(am), data=mtcars)
summary(fit2)
res2 = residuals(fit2)
plot(jitter(res2)~jitter(mpg), ylab="Residuals", xlab="mpg", data=mtcars)
abline(0,0)
```
  
__Multiple R-squared:  0.8428__
  
```{r fit3, echo=TRUE}
fit3 <- lm( mpg ~ ., data=mtcars)
summary(fit3)
res3 = residuals(fit3)
plot(jitter(res3)~jitter(mpg), ylab="Residuals", xlab="mpg", data=mtcars)
abline(0,0)
```
  
__Multiple R-squared:  0.869__

#### Anova
```{r anova, echo=TRUE}
anova(fit1, fit2)
anova(fit2, fit3)
```
\newpage

## 4. Regression Trees

``` {r rt0, echo=TRUE}
library(rpart)
rt0 <- rpart(mpg ~ .,method="anova", data=mtcars)
plotcp(rt0)
printcp(rt0)
summary(rt0)

# create additional plots
par(mfrow=c(1,2)) # two plots on one page
rsq.rpart(rt0) # visualize cross-validation results 

# plot tree 
plot(rt0, uniform=TRUE,main="Classification Tree for mtcars")
text(rt0, use.n=TRUE, all=TRUE, cex=.8)
```

``` {r rt1, echo=TRUE}
rt1 <- rpart(mpg ~ hp + wt + drat + as.factor(am),method="anova", data=mtcars)
plotcp(rt1)
printcp(rt1)
summary(rt1)
# create additional plots
par(mfrow=c(1,2)) # two plots on one page
rsq.rpart(rt1) # visualize cross-validation results 

# plot tree 
plot(rt1, uniform=TRUE,main="Classification Tree for mtcars")
text(rt1, use.n=TRUE, all=TRUE, cex=.8)
```