---
title: "mlearn310_hw3_3_SVM"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=TRUE}
library(e1071)
library(caret)
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data
```{r load_data, echo=TRUE}
mushroom=read.csv(url("https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.data"), header = FALSE)
names(mushroom) <- c("class", "cap-shape", "cap-surface", "cap-color", "bruises", "odor", "gill-attachment", "gill-spacing", "gill-size", "gill-color", "stalk-shape", "stalk-root", "stalk-surface-above-ring", "stalk-surface-below-ring", "stalk-color-above-ring", "stalk-color-below-ring", "veil-type", "veil-color", "ring-number", "ring-type", "spore-print-color", "population", "habitat")
nrow(mushroom)
mushroom = na.omit(mushroom)
mushroom$"veil-type" = NULL
nrow(mushroom)
summary(mushroom)
split = createDataPartition(y=mushroom$class, p = 0.8, list=FALSE)
mushroom_train = mushroom[split,]
mushroom_test = mushroom[-split,]
```

## SVM - Kernel: Linear

```{r svm_kernel_linear, echo=TRUE}
svm_model_kernel_linear = best.tune(svm, class ~., data = mushroom_train, kernel ="linear")
svm_model_kernel_linear
pred_mushroom_class = predict(svm_model_kernel_linear, mushroom_test)
confusionMatrix(table(pred_mushroom_class, mushroom_test$class))
```

## SVM - Kernel: Poly

```{r svm_kernel_poly, echo=TRUE}
svm_model_kernel_poly = best.tune(svm, class ~., data = mushroom_train, kernel ="polynomial")
svm_model_kernel_poly
pred_mushroom_class = predict(svm_model_kernel_poly, mushroom_test)
confusionMatrix(table(pred_mushroom_class, mushroom_test$class))
```

### SVM - Kernel: Radial

```{r svm_kernel_radial, echo=TRUE}
svm_model_kernel_radial = best.tune(svm, class ~., data = mushroom_train, kernel ="radial")
svm_model_kernel_radial
pred_mushroom_class = predict(svm_model_kernel_radial, mushroom_test)
confusionMatrix(table(pred_mushroom_class, mushroom_test$class))
```

# Comments: The no.of Support vectors for kernels : Linear < Radial < Polynomial
# Comments: The Accuracy  for kernels : Linear & Radial = 1  Polynomial =  0.9951
# Comments: The specificity for all 3 kernles : 1

## SVM - Kernel: Linear, with Cost 

```{r svm_kernel_linear_cost, echo=TRUE}
svm_model_kernel_linear_cost = best.tune(svm, class ~., data = mushroom_train, kernel ="linear", ranges = list(cost = c(0.001, 0.01, 0.1, 1)))
svm_model_kernel_linear_cost
pred_mushroom_class = predict(svm_model_kernel_linear_cost, mushroom_test)
confusionMatrix(table(pred_mushroom_class, mushroom_test$class))
```

## SVM - Kernel: Poly, with Cost 

```{r svm_kernel_poly_cost, echo=TRUE}
svm_model_kernel_poly_cost = best.tune(svm, class ~., data = mushroom_train, kernel ="polynomial", ranges = list(cost = c(0.001, 0.01, 0.1, 1)))
svm_model_kernel_poly_cost
pred_mushroom_class = predict(svm_model_kernel_poly_cost, mushroom_test)
confusionMatrix(table(pred_mushroom_class, mushroom_test$class))
```

### SVM - Kernel: Radial, with Cost 

```{r svm_kernel_radial_cost, echo=TRUE}
svm_model_kernel_radial_cost = best.tune(svm, class ~., data = mushroom_train, kernel ="radial", ranges = list(cost = c(0.001, 0.01, 0.1, 1)))
svm_model_kernel_radial_cost
pred_mushroom_class = predict(svm_model_kernel_radial_cost, mushroom_test)
confusionMatrix(table(pred_mushroom_class, mushroom_test$class))
```

# Comments: The no.of Support vectors for kernels : Linear < Radial < Polynomial
# Comments: The Accuracy  for kernels : Linear &  Radial = 1  & Polynomial =  0.9951
# Comments: The specificity for all 3 kernles : 1